1.3 Meet R - R Practice (Answers)

### 2019-09-06 content/assignment/00-preliminary-survey.Rmd
Add answer keys (web, pdf) for R practice 1.3

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)

>>>>

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)
- [<i class="fas fa-file-pdf"></i> `Answer Key (PDF)`](/homeworks/00-preliminary-survey-answers.html)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/homeworks/00-preliminary-survey-answers-pdf.pdf)

### 2019-09-06 content/r/03-r-practice.Rmd
Add answer keys (web, pdf) for R practice 1.3

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```
- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/r/03-r-practice.pdf)
- [<i class="fas fa-file-pdf"></i> `Answer Key`](/r/03-r-practice-answers.pdf)
- [<i class="fas fa-registered"></i> `R Script`](/r/03-r-practice-answers.R)

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```
- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/r/03-r-practice.pdf)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](r/03-r-practice-answers.html)
- [<i class="fas fa-file-pdf"></i> `Answer Key (PDF)`](/r/03-r-practice-answers-pdf.pdf)
- [<i class="fas fa-registered"></i> `R Script`](/r/03-r-practice-answers.R)

### 2019-09-06 static/r/03-r-practice-answers.Rmd
Add answer keys (web, pdf) for R practice 1.3

---
title: "1.3 Meet R - R Practice (Answers)"
author: "Ryan Safner"
date: "ECON 480 - Fall 2019"
output: pdf_document
---

@@

## 1. Work on the following parts:

a. Create a vector called `me` with two objects, your first name, and your last name.

@@

b. Call the vector to inspect it.

@@

c. Confirm it is a character class vector.

@@

## 2. Use R's help functions to determine what the `paste()` function does. Then paste together your first name and last name.

@@

# note you can choose how to separate string objects with the "sep" argument
# for example
paste("Ryan", "Safner", sep="") # no separation
paste("Ryan", "Safner", sep=" ") # separate with a space " " (the default)
paste("Ryan", "Safner", sep="_") # separate with underscore
```
## 3. Create a vector called `my_vector` with all the even integers from 2 to 10.

@@

## 4. Find the mean of `my_vector` with `mean()`.

@@

## 5. Take all the integers from 18 to 763,^[Hint: use the `:` operator to create a sequence from a starting number to an ending number] then get the mean.

@@

### 6. Install `ggplot2`.

@@

### 7. Load `ggplot2` with the `library()` command.

@@

### 8. Get the `str`ucture of the diamonds data frame. What are the different variables and what kind of data does each contain?

@@

### 9. Get summary statistics separately for `carat`, `depth`, `table`, and `price`.

@@

### 10. `color`, `cut`, and `clarity` are categorical variables (factors). Use the `table()` command to generate frequency tables for each.

@@

### 11. Now rerun the `summary()` command on the entire data frame.

@@

### 12. Now look only at (subset) the first 4 diamonds in the dataset.

@@

### 13. Now look only at (subset) the third and seventh diamond in the dataset.

@@

### 14. Now look only at (subset) the second column of the dataset.

```{r}
diamonds[,2] # select all rows, 2nd column
```
### 15. Do this again, but look using the `$` to pull up the second column by name.

```{r}
# second column is called "cut"
diamonds$cut
```

### 16. Now look only at diamonds that have a `carat` greater than or equal to 1.

@@

### 17. Now look only at diamonds that have a VVS1 `clarity`.

@@

### 18. Now look only at dimaonds that have a color of E, F, I, and J.

@@

### 19. Now look only at diamonds that have a `carat` greater than or equal to 1 and a VVS1 `clarity`.

@@

### 20. Get the average price of diamonds in question 18.^[Hints: use your subset command as an argument to the mean function. You will not need a comma here because you are looking for a single row.]

@@

### 21. What is the highest price for a diamond with a 1.0 carat, D color, and VVS1 clarity?

@@

# second column is called "cut"
diamonds$cut

>>>>

---
title: "1.3 Meet R - R Practice (Answers)"
author: "Ryan Safner"
date: "ECON 480 - Fall 2019"
output:
  html_document:
    df_print: paged
    theme: simplex
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango
---

@@

## 1.

#### Work on the following parts:

### a.
#### Create a vector called `me` with two objects, your first name, and your last name.

@@

### b.
#### Call the vector to inspect it.

@@

### c.
#### Confirm it is a character class vector.

@@

## 2.
#### Use R's help functions to determine what the `paste()` function does. Then paste together your first name and last name.

@@

# note you can choose how to separate string objects with the "sep" argument
# for example
paste("Ryan", "Safner", sep="") # no separation
paste("Ryan", "Safner", sep=" ") # separate with a space " " (the default)
paste("Ryan", "Safner", sep="_") # separate with underscore
```
## 3.
#### Create a vector called `my_vector` with all the even integers from 2 to 10.

@@

## 4.
#### Find the mean of `my_vector` with `mean()`.

@@

## 5.
#### Take all the integers from 18 to 763,^[Hint: use the `:` operator to create a sequence from a starting number to an ending number] then get the mean.

@@

### 6. 
#### Install `ggplot2`.

@@

### 7. 
#### Load `ggplot2` with the `library()` command.

@@

### 8.
#### Get the `str`ucture of the diamonds data frame. What are the different variables and what kind of data does each contain?

@@

### 9. 
#### Get summary statistics separately for `carat`, `depth`, `table`, and `price`.

@@

### 10. 
#### `color`, `cut`, and `clarity` are categorical variables (factors). Use the `table()` command to generate frequency tables for each.

@@

### 11. 
#### Now rerun the `summary()` command on the entire data frame.

@@

### 12. 
#### Now look only at (subset) the first 4 diamonds in the dataset.

@@

### 13. 
#### Now look only at (subset) the third and seventh diamond in the dataset.

@@

### 14. 
#### Now look only at (subset) the second column of the dataset.

```{r}
diamonds[,2] # select all rows, 2nd column
```
### 15. 
#### Do this again, but look using the `$` to pull up the second column by name.

```{r, eval=F}
# second column is called "cut"
diamonds$cut # dont' run this, it'll print 53,000 rows!
```

### 16. 
#### Now look only at diamonds that have a `carat` greater than or equal to 1.

@@

### 17. 
#### Now look only at diamonds that have a VVS1 `clarity`.

@@

### 18. 
#### Now look only at dimaonds that have a color of E, F, I, and J.

@@

### 19.
#### Now look only at diamonds that have a `carat` greater than or equal to 1 and a VVS1 `clarity`.

@@

### 20.
#### Get the average price of diamonds in question 18.^[Hints: use your subset command as an argument to the mean function. You will not need a comma here because you are looking for a single row.]

@@

### 21.
#### What is the highest price for a diamond with a 1.0 carat, D color, and VVS1 clarity?

@@

# second column is called "cut"
# diamonds$cut dont' run this, it'll print 53,000 rows!
